---
title: "Applied#9"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#This problem involves the OJ data set which is part of the ISLR package.
```{r}
library(ISLR)
library(tree)
attach(OJ)
dim(OJ)
```
#1.Create a training set containing a random sample of 800 observations, and a test set containing the remaining observations.
```{r}
set.seed(2)
train.set=sample(1:nrow(OJ), 800)
OJ.test=OJ[-train.set,]
dim(OJ)
length(train.set)
dim(OJ.test)
```
#2.Fit a tree to the training data, with Purchase as the response
 and the other variables as predictors. Use the summary() function
 to produce summary statistics about the tree, and describe the
 results obtained. What is the training error rate? How many
 terminal nodes does the tree have?
```{r}
tree.fit=tree(Purchase~., data=OJ, subset=train.set)
summary(tree.fit)
plot(tree.fit)
text(tree.fit, pretty=0)
```
 training error rate=Residual mean deviance:  0.7463 = 591.8 / 793 
 7 terminal nodes
#3.Type in the name of the tree object in order to get a detailed
 text output. Pick one of the terminal nodes, and interpret the
 information displayed.
```{r}
tree.fit
```
#5 Predict the response on the test data, and produce a confusion
 matrix comparing the test labels to the predicted test labels.
 What is the test error rate?
```{r}
yhat.tree = predict(tree.fit,newdata=OJ.test, type="class")
pur.test=OJ[-train.set,"Purchase"]
length(yhat.tree)
length(pur.test)
table(yhat.tree,pur.test)
```
Интерпретация confusion matrix: (событие А= Purchase CH; CH=Event,MM=No Event)
test Error Rate=$(FP+FN)/(TP+TN+FP+FN)$=(69+43)/(114+69+43+44)=0.4148148
TP Rate=$TP/(TP+FN)$=114/(114+43)=0.7261146
FP Rate=$FP/(FP+TN)$=69/(69+44)=0.6106195
Sensitivity=$TP/(TP+FN)$=114/(114+43)=0.7261146
Specificity=$TN/(FP+TN)$=44/(44+69)=0.3893805
 
*6*
Apply the cv.tree() function to the training set in order to
 determine the optimal tree size.
ответ: 9- optimal tree size
(g) Produce a plot with tree size on the x-axis and cross-validated
 classification error rate on the y-axis.
```{r}
cv.oj=cv.tree(tree.fit)
plot(cv.oj$size,cv.oj$dev,type='b')
```
 
 9. This problem involves the OJ data set which is part of the ISLR
 package.
 (a) Create a training set containing a random sample of 800 obser
vations, and a test set containing the remaining observations.
 (b) Fit a tree to the training data, with Purchase as the response
 and the other variables as predictors. Use the summary() function
 to produce summary statistics about the tree, and describe the
 results obtained. What is the training error rate? How many
 terminal nodes does the tree have?
 (c) Type in the name of the tree object in order to get a detailed
 text output. Pick one of the terminal nodes, and interpret the
 information displayed.
 (d) Create a plot of the tree, and interpret the results.
 (e) Predict the response on the test data, and produce a confusion
 matrix comparing the test labels to the predicted test labels.
 What is the test error rate?
 (f) Apply the cv.tree() function to the training set in order to
 determine the optimal tree size.
 
 
 (h) Which tree size corresponds to the lowest cross-validated classification error rate? 
 ответ: prunning wont improve results(residual deviance=cv error rate won't decrease)
```{r}
prune.oj=prune.tree(tree.fit,best=5)
plot(prune.oj)
text(prune.oj,pretty=0)
summary(prune.oj)
```

 (i) Produce a pruned tree corresponding to the optimal tree size
 obtained using cross-validation. If cross-validation does not lead
 to selection of a pruned tree, then create a pruned tree with five
 terminal nodes.