---
title: "Applied#8"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##задача
a classification tree was applied to the Carseats data set after converting Sales into a qualitative response variable. Now we will seek to *predict Sales using regression trees* and related approaches,treating the response as a *quantitative variable.*
```{r}
library(ISLR)
library(MASS)
library(tree)
attach(Carseats)
```

#1  Split the data set into a training set and a test set
```{r}
train.set = sample(1:nrow(Carseats), nrow(Carseats)/2)
test.set=Carseats[-train.set,]
```
#2.Fit a regression tree to the training set.
Plot the tree, and interpret the results. What test MSE do you obtain?
```{r}
reg.tree=tree(Sales~., data=Carseats, subset=train.set)
summary(reg.tree)
plot(reg.tree)
text(reg.tree,pretty=0)
```
deviance is simply the sum of squared errors for the tree
#Use cross-validation in order to determine the optimal level of
 tree complexity. Does pruning the tree improve the test MSE?
```{r}
cv=cv.tree(reg.tree)
plot(cv$size,cv$dev,type='b')
```
dev-corresponding to size error rate
```{r}
prune=prune.tree(reg.tree,best=5)
plot(prune)
text(prune,pretty=0)
summary(prune)
```
significant decrease in test mse after pruning -Residual mean deviance:  4.41 = 860 / 195 
#Use the bagging approach in order to analyze this data.
What test MSE do you obtain? Use the importance() function to determine which variables are most important.
**bagging = case of a random forest with m=p**
```{r}
library(randomForest)
bag=randomForest(Sales~.,data=Carseats, subset=train.set, mtry=13, importance=TRUE)
bag
```
*mtry=13* indicates that *all* 13 predictors should be considered
 for each split of the tree —in other words, that bagging should be done.
```{r}
importance(bag)
```
#Use random forests to analyze this data. What test MSE do you
 obtain? Use the importance() function to determine which vari
ables are most important. Describe the effect of m,thenumberof
 variables considered at each split, on the error rate
 obtained.
```{r}
sales.rf=randomForest(Sales~., data=Carseats, subset=train.set, mtry=6, importance=TRUE)
yhat.rf = predict(sales.rf,newdata=Carseats[-train.set,])
Carseats.test=Carseats[-train.set,"Sales"]
# fix(Carseats)
mean((yhat.rf-Carseats.test)^2)
```
that's the test MSE
```{r}
importance(sales.rf)
```

