---
title: "non-linear models(Polynomial;Step Function)+ ANOVA для выбора степени полинома (альтернатива CV)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
attach(Wage)
library(MASS)
fix(Wage)
```

*1* Polynomial Regression and Step Functions
```{r}
poly.fit=lm(wage~poly(age,4), data=Wage)
coef(summary(poly.fit))

```
Этот синтаксис соответствует линейной модели, используя функцию lm(), чтобы предсказать
 размер, использующий полиномий четвертой степени в возрасте: poly(age,4)
  Функция возвращает матрицу, столбцы которой являются основанием ортогональных полиномов, другими словами каждый столбец является линейным ортогональной комбинацией переменных age^1, age^2, age^3, age^4.
```{r alternative fitting methods}
poly.fit2a=lm(wage~age+I(age^2)+I(age^3)+I(age^4),data=Wage)
coef(summary(poly.fit2a))
# I(x^n)- wrapper or cbind()
poly.fit2b=lm(wage~cbind(age,age^2,age^3,age^4),data=Wage)
coef(summary(poly.fit2b))
```
*2* predict()
```{r}
age.limits=range(age)
age.grid=seq(from=age.limits[1],to=age.limits[2])
length(age.grid)

poly.pred=predict(poly.fit,newdata=list(age=age.grid),se=TRUE)
se=cbind(poly.pred$fit+2*poly.pred$se.fit,poly.pred$poly.fit-2*poly.pred$se.fit)
length(se)

```
create a grid of values for age at which we want predictions
*3* plot
```{r}
 par(mfrow=c(1,2),mar=c(4.5,4.5,1,1),oma=c(0,0,4,0))
 plot(age,wage,xlim=age.limits,cex=.5,col="darkgrey")
 title("Degree-4 Polynomial",outer=T)
 lines(age.grid,poly.pred$fit,lwd=2,col="blue")
 matlines(age.grid,se,lwd=1,col="red",lty=3)
```
plot the data and add the fit from the degree-4 polynomial.

##Hypothesis testing: which degree of polynomial to choose? (alternative to CV)
*1* fit models from linear to poly(age,5) and seek simplest model sufficient to explain wage and age relationship
```{r}
ln.fit= lm(wage~age, data=Wage)
poly2.fit=lm(wage~poly(age,2), data=Wage)
poly3.fit=lm(wage~poly(age,3), data=Wage)
poly4.fit=lm(wage~poly(age,4), data=Wage)
poly5.fit=lm(wage~poly(age,5), data=Wage)

```

*2* anova()
```{r}
anova(ln.fit,poly2.fit,poly3.fit,poly4.fit,poly5.fit)
```

analysis of variance using F-test, $H~0$: model $M~0$ is sufficient to explain the data 
against the $H~1$ alternative hypothesis that a more complex model M2 is required.
(netsed Models=  the predictors in M1 must be a  subset of the predictors in M2)
*result*
 The $p-value=< 2.2e-16$ comparing the linear Model 1 to the quadratic Model 2 is
 essentially zero(<10−15)=linear fit is not sufficient (reject the null hypothesis $H~0$).
 p-value comparing the quadratic Model 2 to the cubic Model 3 is very low ($0.001679 **$), so the quadratic fit is also insufficient.
 The p-value comparing the cubic and degree-4 polynomials,Model 3 and Model 4,=$ 0.051046$,
 while the degree-5 polynomial Model 5 seems unnecessary because its p-value is $0.37$.
 
 Вывод:cubic or quadratic polynomial- reasonable fit to the data
 
## Задача: predict whether an individual earns > $250,000 per year.
*1*  create the appropriate response vector+apply the glm() function
 using family="binomial" in order to fit a polynomial logistic regression
 model
```{r}
bin.fit=glm(I(wage>250)~poly(age,4),data=Wage,family=binomial)
```
*2* predict()
```{r}
bin.pred=predict(bin.fit,newdata=list(age=age.grid),se=T)
bin.fit
```
*3* transform to calculate confidence intervals
```{r}
pfit=exp(bin.pred$fit)/(1+exp(bin.pred$fit))
se.bands.logit = cbind(bin.pred$fit+2*bin.pred$se.fit, bin.pred$fit-2*bin.pred$se.fit)
se.bands = exp(se.bands.logit)/(1+exp(se.bands.logit))
length(se.bands)
length(age.grid)
```
we get predictions and standard errors for logit model ($log (Pr(Y =1|X)/(1 −Pr(Y =1|X)) =Xβ,$)
in form of $X\hat β$
to obtain confidence intervals for $Pr(Y =1|X)$, we use the transformation
$Pr(Y =1|X)= exp(Xβ)/(1+exp(Xβ))$

*4* plot()
```{r}
plot(age,I(wage>250),xlim=age.limits,type="n",ylim=c(0,.2))
points(jitter(age), I((wage>250)/5),cex=.5,pch="|",col="darkgrey")
lines(age.grid,pfit,lwd=2, col="blue")
length(pfit)
length(age.grid)
length(se.bands)
se1=se.bands[-c(64:126)]
length(se1)
lines(age.grid,se1,lwd=1,col="green",lty=3)
```
*Step function* fit
```{r}
table(cut(age,4))
step.fit=lm(wage~cut(age,4),data=Wage)
coef(summary(step.fit))
```
cut() автоматически выбирает $age$ cutpoints: 33.5; 49; 64.5 
Функция cut() возвращает ordered categorical variable;
Функция lm() создаетт set of dummy variables(фиктивные переменные) для регрессии.

*predict()*
```{r}
step.pred=predict(step.fit, newdata=list(age=age.grid),se=T)

```
*plot()*
```{r}
par(mfrow=c(1,2),mar=c(4.5,4.5,1,1),oma=c(0,0,4,0))
plot(age,wage,xlim=age.limits,cex=.5,col="darkgrey")
title("Step Function",outer=T)
lines(age.grid,step.pred$fit,lwd=2,col="blue")
matlines(age.grid,se,lwd=3,col="green",lty=3)
```


