---
title: "NONLINEARapplied"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
library(gam)
attach(Wage)
library(e1071)
library(boot)
agelims=range(age)
age.grid=seq(from=agelims[1],to=agelims[2])
```

## условие
In this exercise, you will further analyze the Wage data set considered
 throughout this chapter.
 (a) Perform *polynomial regression* to predict wage using age.
 Use cross-validation to select the optimal degree d for the polynomial.
 What degree was chosen, and how does this compare to the results of hypothesis testing using ANOVA?
 Make a plot ofthe resulting polynomial fit to the data.
*1* fit wage~poly(age,d)+ select d via CV
```{r polynom degree }
library(boot)
 set.seed(17)
 cv.error.10=rep(0,10)
 for (i in 1:10){
 glm.fit=glm(wage~poly(age,i),data=Wage)
 cv.error.10[i]=cv.glm(Wage,glm.fit,K=10)$delta[1]
 }
 cv.error.10
```

 
 
 
 (b) Fit a step function to predict wage using age, and perform cross
validation to choose the optimal number of cuts. Make a plot of
 the fit obtained.
```{r step fun}
table(cut(age,4))
step.fit=lm(wage~cut(age,4),data=Wage)
coef(summary(step.fit))
```

```{r}
pred=predict(step.fit,newdata=list(age=age.grid),se=T)
plot(age,wage,col="gray")
lines(age.grid,pred$fit,lwd=2)
```
 
 